Comparing OTU quality across clustering strategies

### 2021-07-17 exploratory/2021/algorithm_diagram.Rmd
Attempt to fix otu renumbering
Fix bugs to renumber OTUs
Fix bugs after refactor... i think

```{r ggraph_exp, fig.dim=c(6,5), dpi=300}
plot_graph <- function(graph) {
  create_layout(graph, 'linear', sort.by = id) %>% 
  ggraph() +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm'),
                              type = 'closed'),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(-2, 'mm')
                ) +
  geom_edge_loop(aes(span = 1, direction = 270, strength = 0.2, color = is_loop)) +
  geom_node_label(aes(label = name)) +
    scale_edge_color_manual(values = c('white')) +
  theme_void() +
  theme(plot.margin=unit(x=c(0,0,10,0), units="pt"),
        legend.position = 'none')
}

@@

## maybe I'll do everything in python until the actual plotting step

@@

```{r optifit_example, fig.dim=c(6,5), dpi=300}
g <- tbl_graph(nodes = optifit_iters[[1]]$nodes,
               edges = optifit_iters[[1]]$edges)
plot_graph(g)
```

>>>>

```{r ggraph_exp, fig.dim=c(6,5), dpi=300}
plot_graph <- function(graph) {
  create_layout(graph, 'linear', sort.by = id) %>% 
  ggraph() +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm'),
                              type = 'closed'),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(-2, 'mm')
                ) +
  geom_edge_loop(aes(#span = 1, strength = 0.2, direction = 270, 
                     color = is_loop)) +
  geom_node_label(aes(label = name)) +
    scale_edge_color_manual(values = c('black')#c('white')
                            ) +
  theme_void() +
  theme(plot.margin=unit(x=c(0,0,10,0), units="pt"),
        legend.position = 'none')
}

@@

## do backend in python until the actual plotting step

@@

```{r optifit_example, fig.dim=c(6,5), dpi=300}
tbl_graph(nodes = optifit_iters[[1]]$nodes,
          edges = optifit_iters[[1]]$edges) %>% 
  plot_graph()
```
